Forecasting the Changing Dynamics of US Energy Product Exports to OECD Markets: The Role of the Russian-Ukraine Conflict and Future Scenarios

### 2023-05-19 report_Tomo editinta.Rmd
.

crude_oil_bx  %>% 
  features(diff_total_exports, unitroot_kpss)

@@

crude_oil_bx %>% ACF(diff_total_exports) %>% 
  autoplot() + labs(title = "ACF of stationar crude oil exports")

crude_oil_bx %>% PACF(diff_total_exports) %>% 
  autoplot() + labs(title = "PACF of stationar crude oil exports ")
```

>>>>

crude_oil_bx  %>% 
  features(diff_total_exports, unitroot_kpss)
crude_oil_bx %>% autoplot(diff_total_exports)

@@

crude_oil_bx %>%gg_tsdisplay(diff_total_exports, plot_type = "partial")
